IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-04-27 response.tex

		\begin{point}
			Authors assumed the unrealistic situation: the channels are assumed to be perfectly known. However, in practice, the channel should be estimated, e.g., as studied in \cite{You2019,Kang2020}. It would be much better to discuss the channel estimation issue by citing the above references.
			\label{pt:3.4}
		\end{point}

		\begin{response}
			We have added those citations and considered the influence of imperfect cascaded CSIT on the R-E performance. The reviewer is referred to Response \ref{re:1.1} for details. Simulation result in Fig.~\ref{fi:re_csi} demonstrates the robustness of the proposed joint waveform, active and passive beamforming algorithm to cascaded CSIT inaccuracy with different number of IRS elements.
			\label{re:3.4}
		\end{response}

		\begin{point}
			More simulation results should be added to better and aggregately validate the effectiveness of the proposed method.
			\label{pt:3.5}
		\end{point}

		\begin{response}
			Thank you for the suggestion. On top of the previous version, we have introduced two closed-form adaptive waveform design and compared the results with the original BCD Algorithm~\ref{M-al:bcd}. Fig.~\ref{fi:re_noise}--\ref{fi:re_reflector} demonstrate that the LC-BCD Algorithm~\ref{al:lc_bcd} achieves near-optimal performance under different configurations. Moreover, we have investigated in Fig.~\ref{fi:re_csi} and \ref{fi:re_quantization} the impact of imperfect cascaded CSIT and quantized IRS on the achievable R-E region. It can be concluded that the proposed algorithms are robust to CSIT inaccuracy of the cascaded link, and even $b=1$ (i.e. two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS. These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
